XS-FACE preliminary analysis

### 2018-01-10 analysis-main/main_analyses_bll.Rmd

---
title: "XSFACE Analyses"
author: "Mike Frank, continued Bria Long"
date: "July 14, 2016; January 8, 2018"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
    code_folding: hide
---

```{r}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = TRUE)
```

```{r}
rm(list=ls())
library(readr)
library(dplyr)
library(tidyr)
library(langcog)
library(ggplot2)
# library(lubridate)
```

@@

```{r}
d$face_num<-as.numeric(d$is_face=="True")

mss <- d %>%
  group_by(age.grp, subid) %>%
  filter(!is.na(face_num)) %>% # filter out NA values
  summarise(face = mean(face_num)) %>%
  group_by(age.grp)

@@

```{r, d}

mss <- d %>%
  filter(!is.na(age.at.test)) %>%
  filter(!is.na(face_num)) %>%
  group_by(subid, age.at.test) %>%
  summarise(face = mean(face_num)) %>%
  left_join(demo) %>%
  mutate(len = as.numeric(lubridate::as.duration(lubridate::ms(len))))

@@

```{r}
d <- d %>%
  group_by(subid) %>%
  filter(!is.na(face_num)) %>%
  mutate(face_avg = zoo::rollapply(data = face_num, 
                                   width = 30*10, # 10s window
                                   FUN = mean, 
                                   align = "right", 
                                   fill = NA, 
                                   na.rm = TRUE))

@@

```{r}
mss <- d %>%
  filter(!is.na(posture)) %>%
  filter(!is.na(face_num)) %>%
  group_by(age.grp, posture, subid) %>%
  summarise(face = mean(face_num)) %>%
  group_by(age.grp)

@@

```{r}
mss <- d %>%
  filter(!is.na(orientation)) %>%
  filter(!is.na(face_num)) %>%
  group_by(age.grp, orientation, subid) %>%
  summarise(face = mean(face_num)) %>%
  group_by(age.grp)

@@

```{r}
mss <- d %>%
  filter(!is.na(posture) & !is.na(orientation) & !is.na(face_num)) %>%
  group_by(age.grp, posture, orientation, subid) %>%
  summarise(face = mean(face_num)) %>%
  group_by(age.grp)

@@

<!-- # Naming data -->

<!-- Need some helper functions to merge in namings.  -->

<!-- ```{r} -->
<!-- source("helper.R") -->
<!-- ``` -->

<!-- ```{r} -->
<!-- namings <- d %>% -->
<!--   group_by(subid) %>% -->
<!--   do(summarize.naming(.)) %>% -->
<!--   left_join(demo %>% select(subid, gender, age.at.test, len)) -->
<!-- ``` -->

<!-- First examine: how many namings do we have, generally?  -->

<!-- ```{r} -->
<!-- naming_rate <- namings %>% -->
<!--   group_by(subid, age.grp, age.at.test) %>% -->
<!--   summarise(num = n(),  -->
<!--             len = len[1]) %>% -->
<!--   mutate(rate = num / (as.numeric(lubridate::as.duration(lubridate::ms(len)))/60))  -->

<!-- ggplot(naming_rate,  -->
<!--        aes(x = age.at.test, y = rate)) + -->
<!--   geom_point() +  -->
<!--   geom_smooth(span = 1) +  -->
<!--   ylab("Namings per minute") +  -->
<!--   xlab("Age (months)") +  -->
<!--   theme_bw()  -->
<!-- ``` -->

<!-- Break down by novel and familiar.  -->

<!-- ```{r} -->
<!-- naming_rate_familiarity <- namings %>% -->
<!--   group_by(subid, familiarity, age.at.test) %>% -->
<!--   summarise(num = n(),  -->
<!--             len = len[1]) %>% -->
<!--   mutate(rate = num / (as.numeric(lubridate::as.duration(lubridate::ms(len)))/60)) -->

<!-- ggplot(naming_rate_familiarity,  -->
<!--        aes(x = age.at.test, y = rate, col = familiarity)) + -->
<!--   geom_point() +  -->
<!--   geom_smooth(span = 1) +  -->
<!--   ylab("Namings per minute") +  -->
<!--   xlab("Age (months)") +  -->
<!--   theme_bw()  -->
<!-- ``` -->

<!-- Item effects just for fun.  -->

<!-- ```{r} -->
<!-- namings %>% -->
<!--   group_by(subid, name, familiarity, age.at.test) %>% -->
<!--   summarise(num = n(),  -->
<!--             len = len[1]) %>% -->
<!--   mutate(rate = num / (as.numeric(lubridate::as.duration(lubridate::ms(len)))/60)) %>% -->
<!--   ggplot(aes(x = age.at.test, y = rate, col = name)) + -->
<!--   geom_point() +  -->
<!--   facet_grid(.~familiarity) +  -->
<!--   geom_smooth(span = 1) +  -->
<!--   ylab("Namings per minute") +  -->
<!--   xlab("Age (months)") +  -->
<!--   theme_bw()  -->
<!-- ``` -->

<!-- # Namings and face detections -->

<!-- ## Are there more faces during naming instances?  -->

<!-- ## Are there more faces before or after naming instances?  -->

<!-- ```{r} -->
<!-- #   sb <- ddply(d,~subid, summarize.naming, window=c(-3,0)) -->
<!-- #   sa <- ddply(d,~subid, summarize.naming, window=c(0,3)) -->
<!-- #   sb$window <- "before" -->
<!-- #   sa$window <- "after" -->
<!-- #   s <- rbind(sb,sa) -->
<!-- #   s$window <- factor(s$window) -->
<!-- #    -->
<!-- # #   d <- subset(d,!is.na(time)) -->
<!-- # #   s <- ddply(d,~subid, summarize.naming, window=c(-3,3)) -->
<!-- #    -->
<!-- #   s$first.instance <- s$naming.instance == 1 -->
<!-- #   s$log.instance <- round(log10(s$naming.instance)*4)/4 -->
<!-- #   s$binned.instance <- 10^(round(log10(s$naming.instance)*4)/4) -->
<!-- #   s$face.logical <- s$face != 0 -->
<!-- #    -->
<!-- #   ## try plotting individuals -->
<!-- #   mss <- ddply(s,~subid+age.grp+window,summarise, -->
<!-- #                face = na.mean(face)) -->
<!-- ```   -->

<!-- ```{r} -->
<!--   # qplot(age.grp,face,colour=window, -->
<!--   #       xlab="Age (Months)",ylab="Proportion faces detected in window", -->
<!--   #       data=mss,geom=c("point")) +  -->
<!--   #   scale_x_continuous(breaks=c(8,12,16)) + -->
<!--   #   geom_smooth() -->
<!-- ``` -->

@@

<!-- ```{r} -->
<!-- ggplot(ms,  -->
<!--        aes(x = naming.instance, y = mean, col = familiarity)) + -->
<!--   geom_point() +  -->
<!--   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +  -->
<!--   geom_smooth(se = FALSE) +  -->
<!--   facet_grid(~age.grp) +  -->
<!--   xlim(c(0,20)) +  -->
<!--   scale_color_solarized() +  -->
<!--   theme_bw() -->

<!-- ```{r} -->

<!-- #   ## now calculate differences from base rate -->
<!-- #   n <- ddply(s,~subid+age.grp,summarise, -->
<!-- #              face = na.mean(face)) -->
<!-- #    -->
<!-- #   n$br <- ddply(d,~subid+age.grp,summarise, -->
<!-- #               face=na.mean(face))$face -->
<!-- #    -->
<!-- #   n$br.diff <- n$face - n$br -->
<!-- #    -->
<!-- # #   pdf("~/Projects/xsface/writeup/figures/naming_faces_diff.pdf",width=4,height=3) -->
<!-- #   qplot(age.grp,br.diff,position=position_jitter(.2), -->
<!-- #         data=subset(n,age.grp>4),xlab="Age (Months)",ylab="Face detections relative to base rate") +  -->
<!-- #     scale_x_continuous(breaks=c(8,12,16,20)) + -->
<!-- #     geom_abline(slope=0,intercept=0,lty=2) +  -->
<!-- #     stat_summary(fun.data="mean_cl_boot",color="red") -->
<!-- # #   dev.off() -->
<!-- ``` -->

>>>>

---
title: "XSFACE Analyses"
author: "Mike Frank; continued by Bria Long"
date: "July 14, 2016; January 8, 2018"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
    code_folding: hide
---

```{r}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = TRUE)
options(error = browser)
```

```{r}
rm(list=ls())
library(readr)
library(dplyr)
library(tidyr)
library(langcog)
library(ggplot2)
library(lubridate)
```

@@

```{r}

mss <- d %>%
  group_by(age.grp, subid) %>%
  summarise(face = mean(face)) %>%
  group_by(age.grp)

@@

```{r}
mss <- d %>%
  filter(!is.na(age.at.test)) %>%
  group_by(subid, age.at.test) %>%
  summarise(face = mean(face)) %>%
  left_join(demo) %>%
  mutate(len = as.numeric(lubridate::as.duration(lubridate::ms(len))))

@@

```{r}
d <- d %>%
  group_by(subid) %>%
  filter(!is.na(face)) %>%
  mutate(face_avg = zoo::rollapply(data = face, 
                                   width = 30*10, # 10s window
                                   FUN = mean, 
                                   align = "right", 
                                   fill = NA, 
                                   na.rm = TRUE))

@@

```{r}
mss <- d %>%
  filter(!is.na(posture)) %>%
  filter(!is.na(face)) %>%
  group_by(age.grp, posture, subid) %>%
  summarise(face = mean(face)) %>%
  group_by(age.grp)

@@

```{r}
mss <- d %>%
  filter(!is.na(orientation)) %>%
  group_by(age.grp, orientation, subid) %>%
  summarise(face = mean(face)) %>%
  group_by(age.grp)

@@

```{r}
mss <- d %>%
  filter(!is.na(posture) & !is.na(orientation)) %>%
  group_by(age.grp, posture, orientation, subid) %>%
  summarise(face = mean(face)) %>%
  group_by(age.grp)

@@

# Naming data

Need some helper functions to merge in namings.

```{r}
source("helper.R")
```

```{r}
namings <- d %>%
  group_by(subid) %>%
  do(summarize.naming(.)) %>%
  left_join(demo %>% select(subid, gender, age.at.test, len))
```

First examine: how many namings do we have, generally?

```{r}
naming_rate <- namings %>%
  group_by(subid, age.grp, age.at.test) %>%
  summarise(num = n(),
            len = len[1]) %>%
  mutate(rate = num / as.numeric(as.duration(lubridate::hms(len)) / dminutes())) # bll edits here to wrangle dates

ggplot(naming_rate,
       aes(x = age.at.test, y = rate)) +
  geom_point() +
  geom_smooth(span = 1) +
  ylab("Namings per minute") +
  xlab("Age (months)") +
  theme_bw()
```

Break down by novel and familiar.

```{r}
naming_rate_familiarity <- namings %>%
  group_by(subid, familiarity, age.at.test) %>%
  summarise(num = n(),
            len = len[1]) %>%
  mutate(rate = num / as.numeric(as.duration(lubridate::hms(len)) / dminutes())) # bll edits here to wrangle dates

ggplot(naming_rate_familiarity,
       aes(x = age.at.test, y = rate, col = familiarity)) +
  geom_point() +
  geom_smooth(span = 1) +
  ylab("Namings per minute") +
  xlab("Age (months)") +
  theme_bw()
```

Item effects just for fun.

```{r}
namings %>%
  group_by(subid, name, familiarity, age.at.test) %>%
  summarise(num = n(),
            len = len[1]) %>%
  mutate(rate = num / as.numeric(as.duration(lubridate::hms(len)) / dminutes())) %>%  # bll edits here to wrangle dates
  ggplot(aes(x = age.at.test, y = rate, col = name)) +
  geom_point() +
  facet_grid(.~familiarity) +
  geom_smooth(span = 1) +
  ylab("Namings per minute") +
  xlab("Age (months)") +
  theme_bw()
```

# Namings and face detections

## Are there more faces before or after naming instances?

```{r}
library(plyr)

  sb <- ddply(d,~subid, summarize.naming, window=c(-3,0))
  sa <- ddply(d,~subid, summarize.naming, window=c(0,3))
  sb$window <- "before"
  sa$window <- "after"
  s <- rbind(sb,sa)
  s$window <- factor(s$window)

  # not used, commented out
  # s$first.instance <- s$naming.instance == 1
  # s$log.instance <- round(log10(s$naming.instance)*4)/4
  # s$binned.instance <- 10^(round(log10(s$naming.instance)*4)/4)
  # s$face.logical <- s$face != 0

  ## try plotting individuals
  mss <- ddply(s,~subid+age.grp+window,summarise,
               face = mean(face, na.rm="TRUE"))
```

```{r}
  qplot(age.grp,face,colour=window,
        xlab="Age (Months)",ylab="Proportion faces detected in window",
        data=mss,geom=c("point")) +
    scale_x_continuous(breaks=c(8,12,16)) +
    geom_smooth()
```

@@

<!-- ```{r} -->
<!-- ggplot(ms, -->
<!--        aes(x = naming.instance, y = mean, col = familiarity)) + -->
<!--   geom_point() + -->
<!--   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + -->
<!--   geom_smooth(se = FALSE) + -->
<!--   facet_grid(~age.grp) + -->
<!--   xlim(c(0,20)) + -->
<!--   scale_color_solarized() + -->
<!--   theme_bw() -->
<!-- ``` -->

## Now calculate face detection differences from base rate

```{r}

  n <- ddply(s,~subid+age.grp,summarise,
             face = mean(face, na.rm="TRUE"))

  n$br <- ddply(d,~subid+age.grp,summarise,
              face=mean(face, na.rm="TRUE"))$face

  n$br.diff <- n$face - n$br

#   pdf("~/Projects/xsface/writeup/figures/naming_faces_diff.pdf",width=4,height=3)
  qplot(age.grp,br.diff,position=position_jitter(.2),
        data=subset(n,age.grp>4),xlab="Age (Months)",ylab="Face detections relative to base rate") +
    scale_x_continuous(breaks=c(8,12,16)) +
    geom_abline(slope=0,intercept=0,lty=2) +
    stat_summary(fun.data="mean_cl_boot",color="red")
#   dev.off()
```

### 2018-01-10 analysis-validation/face_detection_analysis.Rmd

Load CSV
```{r, message=FALSE, warning=FALSE}
data1 <- read_csv('/Users/alessandro/workspace/3.csv')
data <- read_csv("../data/final_output/mtcnn_face_detections.csv")
```

@@

Summarize
```{r}
data1 %>%
  #filter(w>100 | is.na(w)) %>%
  distinct(group, video, frame, is_face) %>% # ignore > 1 face detections
  group_by(group) %>%
  summarise(face_frames=sum(is_face=="True"), total=n()) %>%
  mutate(percentage=face_frames/total * 100) %>%
  arrange(group) %>%
  kable
```

```{r}
b <- data %>%
  filter(video=="XS_0801", angle==0, is_face=="True") %>%
  arrange(frame)

>>>>

Load CSV
```{r, message=FALSE, warning=FALSE}
# data1 <- read_csv('/Users/alessandro/workspace/3.csv')
data <- read_csv("../data/final_output/mtcnn2.csv")
```

@@

Summarize
```{r}
data %>%
  #filter(w>100 | is.na(w)) %>%
  distinct(group, video, frame, is_face) %>% # ignore > 1 face detections
  group_by(group) %>%
  summarise(face_frames=sum(is_face=="True"), total=n()) %>%
  mutate(percentage=face_frames/total * 100) %>%
  arrange(group) %>%
  kable
```

# ```{r} # no "angle" in data
# b <- data %>%
#   filter(video=="XS_0801", angle==0, is_face=="True") %>%
#   arrange(frame) 
# 
# ```
